Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Distributed bits in the intro

\section{Introduction}

>>>>

\section{Introduction}
Distributed   applications,  including  batch  processing, streaming, and scale-out databases generate a significant amount of network traffic and a~considerable fraction of their runtime is due to network activity. In this  paper, we study  algorithms  for collocating frequently communicating nodes in a distributed networked systems in an online fashion.
